Stack Safety as a Security Property

### 2020-07-01 main.tex

In this section we will describe stack safety as a formal property. We
begin with our model of knowledge about the program structure\leo{I
  hate this}, and then dive in to local state encapsulation and
well-bracketed control flow.

@@

Formally a code map is a partial function from addresses to a function
identifier drawn from the set \(\FUNIDS\).
  %
\[\codemap \in \CODEMAPS = \WORDS \rightharpoonup \FUNIDS\]

\leo{Visible from assembly}

A call map is a partial function from addresses to a natural number,
the number of arguments of the call.
  %
\[\callmap \in \CALLMAPS = \WORDS \rightharpoonup \mathbb{N}\]

\leo{The two JAL instructions map to 2 (arg + return)}

@@

A return map is simply a predicate on addresses and may be considered
to identify the final jump of the return sequence. An entry map is
likewise a predicate on addresses.
  %
\[\retmap \in \RETMAPS \subseteq \WORDS\]
\[\entmap \in \ENTMAPS \subseteq \WORDS\]

\leo{retmap is the jal + 1}
\leo{entrymap is the ones after the labels}

>>>>

In this section we will describe stack safety as a formal property. We
begin with introducing a running example that will help keep things
concrete throughout this section, continue with our model of
\leo{compiler-provided?} knowledge about the program structure, and
then dive in to formal definitions local state encapsulation and
well-bracketed control flow.

\begin{figure}[b]
  \begin{centering}
    \begin{minipage}{0.5\textwidth}
\begin{verbatim}
f{
  int x, y;
  ...
  y = g(0);
  ...
}

g(x){
  return (x + h(17));
}

h(x){
  return (x + 1);
}
\end{verbatim}
\end{minipage}
\end{centering}
\caption{High-level Program with Simple Nested Calls}
\label{fig:running-program}
\end{figure}

@@

Formally a code map is a partial function from addresses to a function
identifier drawn from the set \(\FUNIDS\).
  %
\[\codemap \in \CODEMAPS = \WORDS \rightharpoonup \FUNIDS\]
%
In our running example, instructions 100-124 correspond to $f$,
instructions 140-196 correspond to $g$, and instructions 200-228
correspond to $h$.

A call map is a partial function from addresses to a natural number,
the number of arguments and return values of the call.
  %
\[\callmap \in \CALLMAPS = \WORDS \rightharpoonup \mathbb{N}\]
%
In our running example, the callmap would contain (at least) two
entries: the word 112 corresponding to the first $\jal$
instruction to $g$, which would map to $2$ as the call has one
argument; and the word 164 also mapping to $2$ corresponding
to the call to $h$.

@@

A return map is simply a predicate on addresses and may be considered
to identify the final jump of the return sequence. An entry map is
likewise a predicate on addresses.
  %
\[\retmap \in \RETMAPS \subseteq \WORDS\]
\[\entmap \in \ENTMAPS \subseteq \WORDS\]
%
In our running example, the return map identifies the $\jalr$
instructions 196 and 224, while the entry map identifies
instructions 140 and 200.
